Text Is All You Need

### 2023-05-04 docs/hes_final/article.qmd
whitespace fixes

Country context inputs consisted of two numerical indicators ('Under-five mortality rate 2019' and 'Adolescent population 2020 Proportion of total population (%) Total' from UNICEF's State of the World's Children report [@sowc]) and three one-hot-encoded categorical indicators (categories of Human Development Index ranges [@hdi], categories of gross national income per capita [@wb], and categories of Fragile States Index ranges[@fsi]).

@@

Our third approach used a pair of transformer models to extract information directly from the GDELT embedding corpus[@vaswani2017attention]. Architecturally, both models are encoder-only transformers, but for simplicity, we will refer to the first of these models as “the encoder” and the second as the “classifier”.

>>>>

Country context inputs consisted of two numerical indicators ('Under-five mortality rate 2019' and 'Adolescent population 2020 Proportion of total population (%) Total' from UNICEF's State of the World's Children report [@sowc]) and three one-hot-encoded categorical indicators (categories of Human Development Index ranges [@hdi], categories of gross national income per capita [@wb], and categories of Fragile States Index ranges [@fsi]).

@@

Our third approach used a pair of transformer models to extract information directly from the GDELT embedding corpus [@vaswani2017attention]. Architecturally, both models are encoder-only transformers, but for simplicity, we will refer to the first of these models as “the encoder” and the second as the “classifier”.
